Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.Rmd
correct the figures in pdf

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     shape == {{shape}},
                     e_sigma == {{e_sigma}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

        # Return a data frame containing p-values of
        # F, RESET, BP and SW tests
        tibble(shape = shape,
               e_sigma = e_sigma,
               x_dist = x_dist,
               n = n,
               effect_size = es,
               F_p_value = mod$test(tmp_dat)$p_value,
               RESET3_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:3, 
                                         power_type = "fitted")$p_value,
               RESET4_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:4, 
                                         power_type = "fitted")$p_value,
               RESET5_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:5, 
                                         power_type = "fitted")$p_value,
               RESET6_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:6, 
                                         power_type = "fitted")$p_value,
               RESET7_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:7, 
                                         power_type = "fitted")$p_value,
               RESET8_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:8, 
                                         power_type = "fitted")$p_value,
               RESET9_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:9, 
                                         power_type = "fitted")$p_value,
               RESET10_p_value = mod$test(tmp_dat, 
                                          test = "RESET", 
                                          power = 2:10, 
                                          power_type = "fitted")$p_value,
               BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
               SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
               boot_id = i)
        }) %>%
  reduce(bind_rows)
  }

@@

        # Get the effect size from the pre-calculated table 
        es <- filter(vi_survey, 
                     a == {{a}}, 
                     b == {{b}},
                     n == {{n}}) %>%
          head(1) %>%
          pull(effect_size)

        # Return a data frame containing p-values of
        # F, RESET, BP and SW tests
        tibble(a = a,
               b = b,
               x_dist = x_dist,
               n = n,
               effect_size = es,
               F_p_value = POLY_MODEL$test(

@@

@@

```{r different-x-dist-poly-power, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 500 times and the corresponding power curves are drawn with transparent grey lines. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests.", dev = 'png', dpi = 450}

>>>>

        # Return a data frame containing p-values of
        # F, RESET, BP and SW tests
        tibble(shape = shape,
               e_sigma = e_sigma,
               x_dist = x_dist,
               n = n,
               F_p_value = mod$test(tmp_dat)$p_value,
               RESET3_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:3, 
                                         power_type = "fitted")$p_value,
               RESET4_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:4, 
                                         power_type = "fitted")$p_value,
               RESET5_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:5, 
                                         power_type = "fitted")$p_value,
               RESET6_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:6, 
                                         power_type = "fitted")$p_value,
               RESET7_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:7, 
                                         power_type = "fitted")$p_value,
               RESET8_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:8, 
                                         power_type = "fitted")$p_value,
               RESET9_p_value = mod$test(tmp_dat, 
                                         test = "RESET", 
                                         power = 2:9, 
                                         power_type = "fitted")$p_value,
               RESET10_p_value = mod$test(tmp_dat, 
                                          test = "RESET", 
                                          power = 2:10, 
                                          power_type = "fitted")$p_value,
               BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
               SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
               boot_id = i)
        }) %>%
  reduce(bind_rows)
  }

@@

        # Return a data frame containing p-values of
        # F, RESET, BP and SW tests
        tibble(a = a,
               b = b,
               x_dist = x_dist,
               n = n,
               F_p_value = POLY_MODEL$test(

@@

```{r}
# rewrite effect size here (if needed)

```

```{r}
# Borrow effect size from the survey
poly_conv_sim <- poly_conv_sim %>%
  left_join(select(filter(vi_survey, type == "polynomial"), shape, e_sigma, n, x_dist, effect_size))

heter_conv_sim <- heter_conv_sim %>%
  left_join(select(filter(vi_survey, type == "heteroskedasticity"), a, b, n, x_dist, effect_size))
```

@@

```{r different-x-dist-poly-power, fig.height = 4, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 500 times and the corresponding power curves are drawn with transparent grey lines. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests.", dev = 'png', dpi = 450}

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.tex
correct the figures in pdf

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 16\% to 100\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable residual
departures can be spotted from the example residual plots.

>>>>

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 10\% to 100\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable residual
departures can be spotted from the example residual plots.
